\begin{rubric}{Employment History}
\entry*[2023 -- Present]%
	\textbf{Quant Developer,} Ping An Bank Co., Ltd.%
	%
	\begin{itemize}
		\item \textbf{Algo Trading Engine (FICC):} Core developer of the bank's FICC algo optimization engine. Built the mathematical models that combine market microstructure signals and generate real-time aggressive/passive order decisions for electronic trading.
		\item \textbf{Bond \& Gold Future Market-Making:} Core developer of the electronic market-making engine. Redesigned the architecture from monolithic optimization to modular market-making logic, reducing execution cycle time by over 90\%.
		\item \textbf{Smart Execution (RFQ):} Developed a binary classifier (informed vs. income trader) using supervised ML; integrated the model with PKIM algo to dynamically adjust quoting strategy per client type.
		\item \textbf{IRR Trading Engine:} Designed and implemented the bond/futures IRR trading engine, including Greeks-sensitive hedging calculations and dual-mode (aggressive/passive) order generation.
		\item \textbf{Production Support:} Maintained live algo instances; collaborated with traders on algo configuration, production issue diagnosis, and on-call support.
	\end{itemize}%

\entry*[2021 -- 2023]%
	\textbf{Quant Developer,} Shenzhen Ping An Comprehensive Financial Services Co., Ltd.%
	%
	\begin{itemize}
		\item \textbf{Swap Algo Trading:} Applied customer-tier logic to swap algo instances; built an Excel-based subscription sheet for swap curve ingestion and algo order generation; validated via backtesting and pushed to production.
		\item \textbf{FX Basis Trading:} Designed the FX basis trading strategy per interest rate parity; verified the pricing formula and deployed the algo trading system; manually placed SOFR instrument orders.
		\item \textbf{Tooling \& Automation:} Enhanced the algo-viewer monitoring dashboard for traders; developed Excel add-in functions (VBA/Python) for internal quant team workflow automation.
		\item \textbf{Quant Research Infrastructure:} Built Python/C++ backtesting and data analysis tooling for the quant research team.
	\end{itemize}%

\end{rubric}